Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-27 SRO_Retest_Analyses.Rmd
cont working on retest exploration

1. Cleaning doesn't seem to make a huge difference except for raw accuracies and hddm non_decision  
2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities  
3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest

```{r}
cor_df%>%
  select(-pearson) %>%
  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
  group_by(var_type, clean_type, var) %>%
  summarise(mean_spearman = mean(spearman, na.rm=T),
            sem_spear = sem(spearman),
            num_vars = n())
```

@@

--------------------------------

Can you get the factor structure for the retest
step 1:Ttest on all measures of T1 for people w and without retest
```{r}

@@

Completion times/days

- First data release email esp to ASU
- Send the spreadsheet with meaningul variables + demographics

>>>>

1. Cleaning doesn't seem to make a huge difference (at least for Spearman correlations) except for raw accuracies and hddm non_decision  
2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities (I'm not sure about the reason for the discrepancy between the number of variables)  
3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest

```{r}
cor_df%>%
  select(-pearson) %>%
  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
  group_by(var_type, clean_type, var) %>%
  summarise(mean_spearman = mean(spearman, na.rm=T),
            sem_spear = sem(spearman),
            num_vars = sum(ifelse(is.na(spearman)==FALSE,1,0))) %>%
  arrange(var_type, -as.numeric(as.factor(clean_type)))
```

@@

# Replicating the factor structure

## Confirm comparability of retest and rest sample

First do a t-test on all measures of T1 for subjects with and without retest to confirm that these two samples do not differ from each other significantly
```{r}
ttest_df = data.frame(t_stat = rep(NA, length(matching_dv_columns)),
                      p_val = rep(NA, length(matching_dv_columns)))

row.names(ttest_df) <- matching_dv_columns

for(i in 1:length(matching_dv_columns)){
  ttest_df[matching_dv_columns[i], 't_stat'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$statistic

  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
}

ttest_df$dv = row.names(ttest_df)
row.names(ttest_df) = seq(1:nrow(ttest_df))
ttest_df$task = 'task'
ttest_df[grep('survey', ttest_df$dv), 'task'] = 'survey'
```

Distribution of t values

```{r warning=FALSE, message=FALSE}
ttest_df %>%
  ggplot(aes(t_stat)) +
  geom_histogram()+
  theme_bw()+
  facet_wrap(~task)
```

**Which variables are significantly different between the two samples (those with and without retest data for T1)?**

A handful of variables. None of them are very strongly different though.

```{r}
ttest_df %>%
  filter(p_val<0.05) %>%
  select(dv, task, t_stat, p_val)
```

Do this again with cleaned data.

## Efa and Cfa

@@

# Completion times/days

# Invited vs. completed retest
